---
title: "Building Blocks - Writing with Data"
author: Juyoung(Rosemary) Hahm
date: 2020-9-13
output: github_document
---
```{r setup, include = FALSE}
library(tidyverse)
```

# Learning assessment 1:
Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?

```{r learning assessment 1, message = FALSE}
sample_df = tibble(
  sample_num = rnorm(500, mean = 1),
  sample_zero = sample_num > 0,
  sample_abs = abs(sample_num)
) 
ggplot(sample_df, aes(x = sample_abs)) + geom_histogram()
sample_medianline = median(pull(sample_df, sample_num))
```
The median of the variable containing absolute values is 
`r round(sample_medianline, digits = 2)`.

# Learning assessment 2:
After the previous code chunk, write a bullet list given the mean, median, and standard deviation of the original random sample.

* Mean of the sample is `r mean(pull(sample_df, sample_num))`. 
* Median of the sample is `r median(pull(sample_df, sample_num)) `.
* Standard deviation of the sample is `r sd(pull(sample_df, sample_num)) `.

# Summary

First we create a dataframe containing variables of four different types.

```{r example_df, message = F}
example_df = tibble(
  vec_numeric = 5:8,
  vec_char = c("My", "name", "is", "Rosemary"),
  vec_logical = c(T,T,T,F),
  vec_factor = factor(c("male", "male", "female", "female"))
)
```

The variable `vec_numeric` has class `r class(pull(example_df, vec_numeric))`, and the variable `vec_factor`has class `r class(pull(example_df, vec_factor))`.


Next, we show the plots of a data frame `plot_df`.

```{r getting started with best practices, message = FALSE}
set.seed(1) 
plot_df = tibble(
  x = rnorm(1000, sd = 0.5),
  y = 1 + 2*x + rnorm(1000),
)
```

The histogram of `plot_df` is:
```{r histogram, message = F}
ggplot(plot_df, aes(x = x)) + geom_histogram()
```

Next, the scatter plot of `y` vs `x` is:
```{r yx_scatter}
ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```


git remote -v

